---
title: "Medialis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    runtime: shiny
---



```{r setup, include=FALSE}

options(shiny.maxRequestSize=30*1024^2)
library(shiny)
library(flexdashboard)
library(shinydashboard)
library(readxl)
library(FactoMineR)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(shiny)
library(tidyverse)
library(FactoMineR)
library(shiny)
library(ggplot2)
library(gridExtra)
library(dplyr)
library(shiny)
library(readxl)
library(ggplot2)
library(reshape2)
  # Define the color palette
cols <- c("red", "blue", "green", "purple", "orange")


```

# HCP specific


Column {data-width=650}
-----------------------------------------------------------------------


```{r}

shinyApp(
  


ui <- fluidPage(
  # Add a light blue background color
  tags$style(HTML("body {background-color: lightblue;}")),
  
  # Make the tab labels bold, change the font, and increase the font size
  tags$head(
    tags$style(HTML("
      .navbar-nav a {
        font-weight: bold;
        font-family: 'Helvetica Neue', sans-serif;
        font-size: 18px;
      }
    "))
  ),
  
  navbarPage(
    # Add icon along with the title in the shinydashboard header
    title <- tags$a(href='',
                    style = "font-weight: bold; text-align: center;",
                    icon("M"),
                    'MEDIALIS: The Shiny App [Variation analyses]', target="_blank"),
    
    
    
    tabPanel("Upload Data",
             fileInput("file", "Choose an Excel file"),
             selectInput("sheet", "Choose a sheet", choices = NULL),
             tableOutput("table")),
    tabPanel("MCA Plot",
             plotOutput("mcaPlot")),
    tabPanel("Scatter Plot",
             plotOutput("scatterPlot")),
    tabPanel("Box Plot 1",
             plotOutput("boxPlot1")),
    tabPanel("Box Plot 2",
             plotOutput("boxPlot2")),
    tabPanel("Simulated Data",
             actionButton("startSimulation", "Start Simulation"),
             plotOutput("simulatedDensityPlot1"),
             plotOutput("simulatedDensityPlot2"),
             plotOutput("simulatedDensityPlot3")),
    tabPanel("Simulated Data Table",
             tableOutput("simulatedDataTable")),
    tabPanel("Simulated Data Boxplot: Country",
             plotOutput("simBoxPlotCountry")),
    tabPanel("Simulated Data Boxplot: Discipline",
             plotOutput("simBoxPlotDiscipline"))
  )
),


server <- function(input, output, session) {
  data <- reactiveVal(NULL)
  
  observeEvent(input$file, {
    req(input$file)
    sheets <- excel_sheets(input$file$datapath)
    updateSelectInput(session, "sheet", choices = sheets)
  })
  
  observeEvent(input$sheet, {
    req(input$file)
    req(input$sheet)
    data(read_excel(input$file$datapath, sheet = input$sheet))
  })
  
  output$table <- renderTable({
    req(data())
    data()
  })
  
  df_mixed <- reactive({
    req(data())
    data() %>%
      dplyr::select(contains("code"))
  })
  
  res_mca <- reactive({
    req(df_mixed())
    # Check if data meets requirements for MCA
    if (ncol(df_mixed()) < 2) {
      stop("Data must have at least two columns for MCA")
    }
    
    if (any(sapply(df_mixed(), function(x) length(unique(x))) < 2)) {
      stop("All columns must have at least two unique values for MCA")
    }
    
    # Perform MCA
    MCA(df_mixed())
  })
  
  output$mcaPlot <- renderPlot({
    req(res_mca())
    # Check if MCA was successful
    if (inherits(res_mca(), "try-error")) {
      plot.new()
      text(0.5, 0.5, paste("Error:", as.character(res_mca())))
      return()
    }
    
    # Plot MCA results
    plot(res_mca())
  })
  
  data_with_pc <- reactive({
    req(data())
    req(res_mca())
    # Check if MCA was successful
    if (inherits(res_mca(), "try-error")) {
      return(data())
    }
    
    # Add principal component scores to data
    data() %>%
      mutate(
        pc1 = res_mca()$ind$coord[, 1],
        pc2 = res_mca()$ind$coord[, 2]
      )
  })
  
  output$scatterPlot <- renderPlot({
    req(data_with_pc())
    # Check if MCA was successful
    if (inherits(res_mca(), "try-error")) {
      plot.new()
      text(0.5, 0.5, paste("Error:", as.character(res_mca())))
      return()
    }
    
    # Create scatter plot
    ggplot(data_with_pc(), aes(x = pc1, y = pc2, color = Discipline)) +
      geom_point() +
      stat_ellipse()
  })
  
  data_with_difference <- reactive({
    req(data_with_pc())
    # Check if MCA was successful
    if (inherits(res_mca(), "try-error")) {
      return(data())
    }
    
    # Calculate difference between first two principal components
    data_with_pc() %>%
      mutate(Difference_PC = pc1 - pc2)
  })
  
  add_p_value <- function(p, formula, sim_data_df) {
    kruskal_res <- kruskal.test(formula, data = sim_data_df)
    p_value <- kruskal_res$p.value
    p_value_formatted <- format(p_value, digits = 3)
    y_coord <- max(sim_data_df$Difference_PC) + 1
    p + annotate("text", x = 4, y = y_coord, label = paste("Kruskal-Wallis test: P-value =", p_value_formatted))
  }
  
  output$boxPlot1 <- renderPlot({
    req(data_with_difference())
    # Check if MCA was successful
    if (inherits(res_mca(), "try-error")) {
      plot.new()
      text(0.5, 0.5, paste("Error:", as.character(res_mca())))
      return()
    }
    
    # Create box plot
    p <- ggboxplot(data_with_difference(), x = "Discipline", y = "Difference_PC",
                   color = "Discipline", palette = "jco",
                   add = "jitter")
    
    # Add p-value to plot
    p_sim_boxplot_discipline <- add_p_value(p, Difference_PC ~ Discipline, data_with_difference())
    
    print(p_sim_boxplot_discipline)  # Note that we need to print the plot explicitly
  })
  
  output$boxPlot2 <- renderPlot({
    req(data_with_difference())
    # Check if MCA was successful
    if (inherits(res_mca(), "try-error")) {
      plot.new()
      text(0.5, 0.5, paste("Error:", as.character(res_mca())))
      return()
    }
    
    # Create box plot
    p <- ggboxplot(data_with_difference(), x = "Country", y = "Difference_PC",
                   color = "Country", palette = "jco",
                   add = "jitter")
    
    # Add p-value to plot
    p_sim_boxplot_country <- add_p_value(p, Difference_PC ~ Country, data_with_difference())
    
    print(p_sim_boxplot_country)  # Note that we need to print the plot explicitly
  })
  
  # Simulation function without mean imputation
  run_simulation <- eventReactive(input$startSimulation, {
    req(data())
    req(res_mca())
    
    n_sim <- 1000
    
    sim_data <- replicate(n_sim, {
      Discipline_sim <- sample(data()$Discipline, size = nrow(data()), replace = TRUE)
      Country_sim <- sample(data()$Country, size = nrow(data()), replace = TRUE)
      pc1_sim <- rnorm(nrow(data()), mean = mean(res_mca()$ind$coord[, 1]), sd = sd(res_mca()$ind$coord[, 1]))
      pc2_sim <- rnorm(nrow(data()), mean = mean(res_mca()$ind$coord[, 2]), sd = sd(res_mca()$ind$coord[, 2]))
      
      sim_df <- data.frame(Discipline = Discipline_sim,
                           Country = Country_sim,
                           pc1 = pc1_sim,
                           pc2 = pc2_sim)
      
      sim_df
    }, simplify = FALSE)
    
    sim_data_df <- do.call(rbind, sim_data)
    sim_data_df$sim_id <- rep(seq_len(n_sim), each = nrow(data()))
    sim_data_df$Difference_PC <- sim_data_df$pc1 - sim_data_df$pc2
    
    sim_data_df
  })
  
  # Create simulated data density plots
  output$simulatedDensityPlot1 <- renderPlot({
    req(input$startSimulation)
    sim_data <- run_simulation()
    
    p1 <- ggplot(sim_data, aes(x = Difference_PC, colour = Country)) +
      geom_density(lwd = 1.2, linetype = 1) + 
      scale_color_manual(values = cols) +
      xlab("Simulated Difference") +
      ylab("Density")
    
    print(p1)
  })
  
  output$simulatedDensityPlot2 <- renderPlot({
    req(input$startSimulation)
    sim_data <- run_simulation()
    
    p2 <- ggplot(sim_data, aes(x = pc1, colour = Country)) +
      geom_density(lwd = 1.2, linetype = 1) + 
      scale_color_manual(values = cols) +
      xlab("Simulated PC1") +
      ylab("Density")
    
    print(p2)
  })
  
  output$simulatedDensityPlot3 <- renderPlot({
    req(input$startSimulation)
    sim_data <- run_simulation()
    
    p3 <- ggplot(sim_data, aes(x = pc2, colour = Country)) +
      geom_density(lwd = 1.2, linetype = 1) + 
      scale_color_manual(values = cols) +
      xlab("Simulated PC2") +
      ylab("Density")
    
    print(p3)
  })
  
  output$simulatedDataTable <- renderTable({
    req(input$startSimulation)
    sim_data <- run_simulation()
    sim_data
  })
  
  # Create box plot for simulated data: Country
  output$simBoxPlotCountry <- renderPlot({
    req(input$startSimulation)
    sim_data <- run_simulation()
    
    # Create box plot
    p <- ggboxplot(sim_data, x = "Country", y = "Difference_PC",
                   color = "Country", palette = "jco",
                   add = "jitter")
    
    # Add p-value to plot
    p_sim_boxplot_country <- add_p_value(p, Difference_PC ~ Country, sim_data)
    
    print(p_sim_boxplot_country)  # Note that we need to print the plot explicitly
  })
  
  # Create box plot for simulated data: Discipline
  output$simBoxPlotDiscipline <- renderPlot({
    req(input$startSimulation)
    sim_data <- run_simulation()
    
    # Create box plot
    p <- ggboxplot(sim_data, x = "Discipline", y = "Difference_PC",
                   color = "Discipline", palette = "jco",
                   add = "jitter")
    
    # Add p-value to plot
    p_sim_boxplot_discipline <- add_p_value(p, Difference_PC ~ Discipline, sim_data)
    
    print(p_sim_boxplot_discipline)  # Note that we need to print the plot explicitly
  })
},
  

options=list(height=1000, weight="100%")
  
)


```


# Item specific


Column {data-width=350}
-----------------------------------------------------------------------


```{r}

shinyApp(
  ui <- fluidPage(
  # Make the tab labels bold, change the font, and increase the font size
  tags$head(
    tags$style(HTML("
      .navbar-nav a {
        font-weight: bold;
        font-family: 'Helvetica Neue', sans-serif;
        font-size: 18px;
      }
    "))
  ),
  
  titlePanel("Medialis Shiny App: Variation analyses"),
  # Add a light blue background color
  tags$style(HTML("body {background-color: lightblue;}")),
  sidebarLayout(
    sidebarPanel(
      fileInput("file", "Choose File"),
      selectInput("sheet", "Choose Sheet", choices = NULL),
      actionButton("start", "Start Analysis"),
      # Add a dropdown to select the reference country
      selectInput("reference_country", "Choose Reference Country", choices = NULL)
    ),
    mainPanel(
      tabsetPanel(
        tabPanel("Plot", 
                 plotOutput("mcaPlot"),
                 downloadButton("downloadPlot", "Download Plot")
        ),
        tabPanel("Descriptive Statistics", 
                 tableOutput("stats"),
                 downloadButton("downloadStats", "Download Statistics")
        ),
        tabPanel("Analysis Data", 
                 tableOutput("data_table"),
                 downloadButton("downloadData", "Download Analysis Data")
        ),
        # New tab panel for "Reference Selection" p-values
        tabPanel("Reference Selection",
                 tableOutput("p_values_table"),
                 downloadButton("downloadPValues", "Download P-Values")
        )
      )
    )
  )
),

server <- function(input, output, session) {
  observeEvent(input$file, {
    updateSelectInput(session, "sheet", choices = excel_sheets(input$file$datapath))
  })
  
  # Populate the reference country dropdown based on the available countries
  observeEvent(input$start, {
    req(input$file)
    req(input$sheet)
    data <- read_excel(input$file$datapath, sheet = input$sheet)
    countries <- c("UK", "Belgium", "France", "Germany", "Italy")
    updateSelectInput(session, "reference_country", choices = countries)
  })
  
  data_list <- eventReactive(input$start, {
    req(input$file)
    req(input$sheet)
    
    # Read in selected sheet and store it in a list
    data_list <- list(read_excel(input$file$datapath, sheet = input$sheet))
    
    # Assign name to the list element
    names(data_list) <- input$sheet
    
    # Function to perform MCA and extract principal components for a specific country
    perform_mca <- function(df, country) {
      df_country <- df %>% dplyr::select(dplyr::contains(country))
      res_mca <- PCA(df_country)
      return(res_mca$ind$coord[, 1:2])
    }
    
    # Loop through countries and perform MCA, calculate differences, and store results in data_list
    countries <- c("UK", "Belgium", "France", "Germany", "Italy")
    for (country in countries) {
      pcs <- perform_mca(data_list[[input$sheet]], country)
      data_list[[input$sheet]][[paste0(country, "_pc1")]] <- pcs[, 1]
      data_list[[input$sheet]][[paste0(country, "_pc2")]] <- pcs[, 2]
      data_list[[input$sheet]][[paste0(country, "_Difference")]] <- pcs[, 1] - pcs[, 2]
    }
    
    # Function to perform Wilcoxon test and get p-value
    perform_wilcox_test <- function(data1, data2) {
      return(wilcox.test(data1, data2, paired = TRUE)$p.value)
    }
    
    # Loop through countries and calculate Wilcoxon test p-values using the selected reference country
    reference_country <- input$reference_country
    if (is.null(reference_country)) {
      reference_country <- "UK"  # Default reference country is UK if not selected
    }
    uk_data <- data_list[[input$sheet]][[paste0(reference_country, "_Difference")]]
    p_values <- list()
    for (country in countries[-which(countries == reference_country)]) {
      country_data <- data_list[[input$sheet]][[paste0(country, "_Difference")]]
      p_values[[paste0(reference_country, "_vs_", country)]] <- perform_wilcox_test(uk_data, country_data)
    }
    
    # Format p-values
    p_value_formatted <- formatC(unlist(p_values), format = "f", digits = 3)
    
    # Create plot
    long_data <- data_list[[input$sheet]] %>%
      dplyr::select(dplyr::contains("_Difference")) %>%
      pivot_longer(cols = everything(), names_to = "Country_Name", values_to = "Difference_Value") %>%
      mutate(Country_Name = gsub("_Difference", "", Country_Name))
    
    p <- ggplot(long_data, aes(x = Country_Name, y = Difference_Value, fill = Country_Name)) +
      geom_boxplot() + geom_jitter(width = 0.2) +
      geom_hline(yintercept = 0, linetype = "dashed") +
      labs(x = "Country", y = "Variation value") +
      scale_fill_discrete(name = "Country") +
      theme_bw() +
      theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
      scale_y_continuous(limits = c(-10, 10), breaks = seq(-10, 10, by = 2))
    
    return(list(p = p, p_values = p_values, long_data = long_data, analysis_data = data_list[[input$sheet]]))
  })
  
  output$mcaPlot <- renderPlot({
    req(data_list())
    data_list()$p
  })
  
  output$stats <- renderTable({
    req(data_list())
    data_list()$long_data %>%
      group_by(Country_Name) %>%
      dplyr::summarize(Median = median(Difference_Value),
                       `25th Percentile` = quantile(Difference_Value, 0.25),
                       `75th Percentile` = quantile(Difference_Value, 0.75)) %>%
      ungroup()
  })
  
  output$data_table <- renderTable({
    req(data_list())
    data_list()$analysis_data
  })
  
  # Render the table of p-values in "Reference Selection" tab
  output$p_values_table <- renderTable({
    req(data_list())
    p_values <- data_list()$p_values
    reference_country <- input$reference_country
    if (is.null(reference_country)) {
      reference_country <- "UK"  # Default reference country is UK if not selected
    }
    data.frame(Country = names(p_values), P_Value = unlist(p_values), Reference_Country = reference_country)
  })
  
  # Download plot
  output$downloadPlot <- downloadHandler(
    filename = function() {
      paste(input$sheet, "_MCA_Plot.png", sep = "")
    },
    content = function(file) {
      ggsave(file, data_list()$p)
    }
  )
  
  output$downloadStats <- downloadHandler(
    filename = function() {
      paste(input$sheet, "_Descriptive_Statistics.csv", sep = "")
    },
    content = function(file) {
      write.csv(data_list()$long_data %>%
                  group_by(Country_Name) %>%
                  dplyr::summarize(Median = median(Difference_Value),
                                   `25th Percentile` = quantile(Difference_Value, 0.25),
                                   `75th Percentile` = quantile(Difference_Value, 0.75)) %>%
                  ungroup(), file)
    }
  )
  
  output$downloadData <- downloadHandler(
    filename = function() {
      paste(input$sheet, "_Analysis_Data.csv", sep = "")
    },
    content = function(file) {
      write.csv(data_list()$analysis_data, file)
    }
  )
  
  # Download p-values table
  output$downloadPValues <- downloadHandler(
    filename = function() {
      paste(input$sheet, "_P_Values.csv", sep = "")
    },
    content = function(file) {
      p_values_table <- data.frame(Country = names(data_list()$p_values), P_Value = unlist(data_list()$p_values))
      write.csv(p_values_table, file)
    }
  )
},


options=list(height=1000, weight="100%")
  
)


```



# Neutrality Modelling


Column {data-width=350}
-----------------------------------------------------------------------


```{r}

Perform_sims <- function(SummDat, prevalence, values){ 
  # Perform_sims <- function(D, prevalence, values){ 
  
  
  # Number of simulations
  n_sim <- 1000
  
  P_Res <- list()
  length(P_Res) <- length(prevalence)
  
  n_P_Res <- list()
  length(n_P_Res) <- length(prevalence) 
  
  # Loop over different prevalence of the disease  
  for(k in 1:3) {
    # Prevalence of severe disease 
    P <- prevalence[k]
    
    # Number of Papers for the disease
    nR <- nrow(SummDat) 
    # NoP <- 10 # Test code 
    
    # Results: design (overlap, missing, etc.,), accuracy (S, C) and misclassification (FN, FP) 
    Res <- matrix(" ", ncol=4, nrow=nR) 
    # The same Results matrix for numbers 
    # n_Res <- matrix(0, ncol=12, nrow=nR) 
    n_Res <- array(0,  dim=c(n_sim, nR, 2)) 
    
    
    # loop over each row in the dataset
    for (j in 1:nR) {
      
      # set seed for reproducibility 
      set.seed(42) 
      
      #-----------------# 
      # PARAMETERS 
      #-----------------# 
      
      # Extract the row "j" data 
      # Sensitivity and Specificity 
      S = SummDat[j,"S"]
      C = SummDat[j,"C"]
      
      # sample size 
      n = SummDat[j,"N_P"] 
      
      # Initalized temporary storage for storing simulation results  
      #    Sim_Mat <- matrix(0, ncol=6, nrow=nsim)
      # intializing false postives and negatives
      PFP = numeric(n_sim) 
      PFN = numeric(n_sim)
      
      
      for(i in 1:n_sim){ 
        
        # Drawing a sample from a population with fixed prevalence 
        D1 = rbinom(1, n, P) # number of severe cases in a sample of size n
        D0 = n - D1 # number of non-severe cases in the sample
        
        # Drawing the test results for the sample with disease severity (D+) 
        # number of those indicated as severe by the design among those whow are severe
        k1 = rbinom(1, D1, S) # number of true positives
        m1 = D1 - k1 # number false negatives
        
        # Drawing the test results for the sample without disease severity (D-) 
        k0 = rbinom(1, D0, C) # number of true negatives 
        m0 = D0 - k0 # number of false positives
        
        # total tested postive 
        tot_p = k1 + m0 
        tot_n = k0 + m1
        
        # misclassification
        pfp = m0 / tot_p # prop. of false postivies 
        pfn = m1 / tot_n 
        
        PFP[i] = pfp
        PFN[i] = pfn 
        
        rm(pfp, pfn, D0, D1, k1, k0, m1, m0) 
        
        # print(i)
        
      }  # end j-loop: over n_sim simulations
      
      qfn <- quantile(PFN, c(0.5, 0.05, 0.95), na.rm = TRUE)
      qfp <- quantile(PFP, c(0.5, 0.05, 0.95), na.rm = TRUE)
      
      # misclassification
      misclass <- c(sprintf("%.2f (%.2f, %.2f)", qfn[1], qfn[2], qfn[3]), 
                    sprintf("%.2f (%.2f, %.2f)", qfp[1], qfp[2], qfp[3]))
      
      # accuracy: Neutrality (Sensitivity, Specificity)
      accur <- sprintf("%.2f (%.2f, %.2f)", (S+C), S, C)  
      
      # design = (Overlap, redundant, miss, irrelevant)
      des = paste0("(", SummDat$X1[j], ", ", SummDat$X2[j], ", ", (SummDat$a[j] - SummDat$X1[j]), ", ", (SummDat$b[j] - SummDat$X2[j]), ")") 
      Res[j,] = c(des, accur, misclass)
      
      # n_misclass = c(qfn[1], qfn[2], qfn[3], qfp[1], qfp[2], qfp[3])
      # n_accur = c(S, C) 
      # n_des = c(SummDat$X1[j], SummDat$X2[j], (SummDat$a[j] - SummDat$X1[j]), (SummDat$b[j] - SummDat$X2[j]))
      # n_Res[j,] = c(n_des, n_accur, n_misclass)
      n_Res[,j,1] = PFP 
      n_Res[,j,2] = PFN 
      
      rm(S, C)
      
    } # end j-loop: over data rows
    
    P_Res[[k]] <- Res 
    n_P_Res[[k]] <- n_Res 
    
  } # end k-loop: over prevalence
  
  if(values=="FALSE") { return(P_Res) }
  if(values=="TRUE") { return(n_P_Res) }
  
} # end of function



shinyApp(
  ui <- fluidPage(
  # # Add icon along with the title in the shinydashboard header
  title <- tags$a(href='',
                  style = "font-weight: bold; text-align: center;",
                  icon("M"),
                  'MEDIALIS: Neutrality Modelling', target="_blank"),
  br(),
  

  # Sidebar with sliders and table
  sidebarLayout(
    sidebarPanel(
      sliderInput("sensitivity1", "Sensitivity 1:", min = 0, max = 1, value = 0.3889, step = 0.01),
      sliderInput("sensitivity2", "Sensitivity 2:", min = 0, max = 1, value = 0.3485, step = 0.01),
      sliderInput("specificity1", "Specificity 1:", min = 0, max = 1, value = 1.0, step = 0.01),
      sliderInput("specificity2", "Specificity 2:", min = 0, max = 1, value = 0.50, step = 0.01),
      sliderInput("samplesize1", "Sample Size 1:", min = 1, max = 1000, value = 92, step = 1),
      sliderInput("samplesize2", "Sample Size 2:", min = 1, max = 1000, value = 92, step = 1),
      numericInput("overlap1", "Overlap (a) for row 1:", value=14),
      numericInput("overlap2", "Overlap (a) for row 2:", value=23),
      numericInput("redundant1", "Redundant (b) for row 1:", value=22),
      numericInput("redundant2", "Redundant (b) for row 2:", value=13),
      numericInput("severe_cases1", "Total severe cases (a) for row 1:", value=14),
      numericInput("severe_cases2", "Total severe cases (a) for row 2:", value=66),
      numericInput("non_severe_cases1", "Total non-severe cases (c) for row 1:", value=78),
      numericInput("non_severe_cases2", "Total non-severe cases (c) for row 2:", value=26),
      sliderInput("prevalence1", "Prevalence Value #1:", min=0, max=1, value=0.20, step=0.01),
      sliderInput("prevalence2", "Prevalence Value #2:", min=0, max=1, value=0.50, step=0.01),
      sliderInput("prevalence3", "Prevalence Value #3:", min=0, max=1, value=0.80, step=0.01)
    ),
    
    # Show plots and summary data
    mainPanel(
      tabsetPanel(
        tabPanel("Plots", plotOutput("plots")),
        tabPanel("Summary Data", tableOutput("summary"))
      )
    )
    
  )
),




# Define server logic
server <- function(input,output){
  
  # Create the new dataset
  SummDat <- reactive({
    data.frame(
      S=c(input$sensitivity1,input$sensitivity2), # Sensitivity values
      C=c(input$specificity1,input$specificity2), # Specificity values
      N_P=c(input$samplesize1,input$samplesize2), # Sample sizes
      X1=c(input$overlap1,input$overlap2), # Overlap values (a)
      X2=c(input$redundant1,input$redundant2), # Redundant values (b)
      a=c(input$severe_cases1,input$severe_cases2), # Total severe cases (a)
      b=c(input$non_severe_cases1,input$non_severe_cases2) # Total non-severe cases (c)
    )
  })
  
  # Define prevalence values
  prevalence <- reactive({
    c(input$prevalence1,input$prevalence2,input$prevalence3)
  })
  
  # Call Perform_sims function
  results <- reactive({
    Perform_sims(SummDat(), prevalence() ,values="TRUE")
  })
  
  # Combine results into a data frame for plotting
  plot_data <- reactive({
    data.frame() %>%
      {
        for(k in seq_along(prevalence())){
          for(j in seq_len(nrow(SummDat()))){
            temp <- data.frame(
              Prevalence=rep(prevalence()[k],nrow(results()[[k]][ ,j ,])),
              FalsePositives=results()[[k]][ ,j ,1],
              FalseNegatives=results()[[k]][ ,j ,2],
              Scenario=rep(ifelse(j==1,"Min","Max"),nrow(results()[[k]][ ,j ,]))
            )
            . <- rbind(. ,temp)
          }
        }
        .
      }
  })
  
  # Summarize data
  summary_data <- reactive({
    plot_data() %>%
      group_by(Prevalence ,Scenario) %>%
      summarize(
        FalsePositives_median=median(FalsePositives),
        FalsePositives_25th=quantile(FalsePositives ,0.25, na.rm = TRUE),
        FalsePositives_75th=quantile(FalsePositives ,0.75, na.rm = TRUE),
        FalseNegatives_median=median(FalseNegatives),
        FalseNegatives_25th=quantile(FalseNegatives ,0.25, na.rm = TRUE),
        FalseNegatives_75th=quantile(FalseNegatives ,0.75, na.rm = TRUE)
      )
  })
  
  # Create the first plot: Comparison of min and max false negative rates vs false positive rates
  plot1 <- reactive({
    ggplot(plot_data(), aes(x=Scenario ,y=FalseNegatives ,fill=Scenario)) +
      geom_boxplot() +
      facet_wrap(~Prevalence ,ncol=3) +
      labs(x="Scenario" ,y="False Negatives" ,fill="Scenario") +
      theme_minimal() +
      ggtitle("Comparison of Min and Max False Negative Rates") +
      scale_x_discrete(labels=c("Min"="Minimum" ,"Max"="Maximum"))
  })
  
  # Create the second plot: Comparison of min and max false positive rates vs false positive rates
  plot2 <- reactive({
    ggplot(plot_data(), aes(x=Scenario ,y=FalsePositives ,fill=Scenario)) +
      geom_boxplot() +
      facet_wrap(~Prevalence ,ncol=3) +
      labs(x="Scenario" ,y="False Positives" ,fill="Scenario") +
      theme_minimal() +
      ggtitle("Comparison of Min and Max False Positive Rates") +
      scale_x_discrete(labels=c("Min"="Minimum" ,"Max"="Maximum"))
  })
  
  output$plots <- renderPlot({
    grid.arrange(plot1(), plot2(), ncol=2)
  })
  
  output$summary <- renderTable({
    summary_data()
  })
},

  options=list(height=1000, weight="100%")
  
)


```


# Heatmap plot CR1


Column {data-width=350}
-----------------------------------------------------------------------



```{r}

library(shiny)
library(gplots)

ui <- fluidPage(
  titlePanel("Barcode Graph"),
  sidebarLayout(
    sidebarPanel(
      fileInput("file", "Upload Data", accept = c(".RData", ".csv")),
      actionButton("plot", "Plot Graph")
    ),
    mainPanel(
      plotOutput("barcode")
    )
  )
)

server <- function(input, output) {
  data <- reactiveVal()
  
  observeEvent(input$file, {
    # Check file format
    if (grepl("\\.RData$", input$file$name)) {
      # Load data from .RData file
      data(load(input$file$datapath))
    } else if (grepl("\\.csv$", input$file$name)) {
      # Read data from .csv file
      data(read.csv(input$file$datapath))
    }
  })
  
  output$barcode <- renderPlot({
    req(data())
    
    # Convert data to matrix
    data_matrix <- as.matrix(data())
    
    # Ensure all values are numeric
    data_matrix <- apply(data_matrix, 2, as.numeric)
    
    col = c("white","#70AD47","#C6E0B4","#FFD966","#00B0F0","#008080","grey","#FFFFF0")
    
    layout(matrix(c(1,2), nrow = 1), widths=c(4/5, 1/5))
    
    heatmap.2(data_matrix,col=col,
              Rowv=FALSE,dendrogram='none',
              Colv=FALSE,vline=0,
              cexRow=1,cexCol=1,srtCol=45,
              ylab="Item Number",
              sepwidth=c(0.0001),sepcolor="grey",
              colsep=1:ncol(data()),rowsep=1:nrow(data()))
    
    par(mar=c(0,0,0,0))
    
    legend(x="top",
           legend=c("Not suggested",
                    "Complete consensus (CI=1.00)",
                    "Consensus+ (CI>0.50)",
                    "Consensus? (CI>=50>CI>0)",
                    "Unique to SH group",
                    "Homo",
                    "Hetero",
                    "N/A"),
           fill=col,cex=0.70,bg="transparent")
  })
}

shinyApp(ui, server)




```



# Guidance Doc


Column {data-width=350}
-----------------------------------------------------------------------


**Statistical methods reporting for manuscript:**

In this analysis, we used data from an Excel file to explore the distribution of observations by Discipline and Country. We created pie charts to visualize the proportion of observations in each group and calculated frequency and percentage tables to summarize the data.

Next, we performed multiple correspondence analysis (MCA) on columns containing “code” string variables to explore the relationships between these categorical variables. MCA is a multivariate statistical technique used to analyze the patterns of association between categorical variables. We extracted the principal component scores for the first two components and created a scatter plot to visualize the individuals on these components.

We then calculated the difference between the first two principal components and performed descriptive analysis by Discipline and Country. We calculated the median and interquartile range (25th and 75th percentiles) for the Difference_PC variable within each group and created box plots to compare the distribution of this difference by Discipline and Country. We used the Kruskal-Wallis test to assess whether there were significant differences in the distribution of the difference between groups.

Next, we performed a simulation study to generate new data based on the observed data. We simulated n_sim new data sets by sampling from normal distributions for the continuous variables (codes, pc1, and pc2) and by randomly sampling with replacement from the observed data for the categorical variables (Discipline and Country). We then combined the simulated data sets into a single data frame and calculated the difference between the first two principal components (pc1 and pc2) for each simulated observation.

We created density plots to visualize the distribution of the simulated Difference_PC, pc1, and pc2 variables by Country. We also created box plots to compare the distribution of the simulated Difference_PC variable by Discipline and Country. We used the Kruskal-Wallis test to assess whether there were significant differences in the distribution of the simulated difference between groups.

To cite R in publications use:
R Core Team (2023). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria.
 URL https://www.R-project.org/.
Packages used for analys:
readxl
tidyverse
rstatix
FactoMineR
gridExtra










